---
title: "CA-V1"
format: html
editor: visual
---

## Introduction

I found this project particularly difficult. I have very little coding experience, with the course being my first time. I have found R Studio more forgiving than the likes of VScode however, as I can run smaller sections/ chunks of code and see if they work while in VScode it seems as though its impossible to move on to another section unless everything is working. I understand the core data analytics finding processes of the module, but I find it challenging finding them through means of coding.

Information on using the following prompts used was found at:

<https://blog.rsquaredacademy.com/working-with-databases-using-r/>

## Installing Packages

I ran into my first round of problems loading these. I then realized I was entering in the wrong brackets.

```{r}
install.packages(c("DBI", "dbplot", "ggplot2", "modeldb", "tidypredict", "config"))
install.packages("readxl")

library(DBI)
library(dbplyr)
library(dplyr)
library(dbplot)
library(ggplot2)
library(modeldb)
library(tidypredict)
library(config)
```

## Connecting to the Database

I couldn't get the assigned download of the database (ICA_2023.sqlite) to display properly in R, so I wrote it out in Excel and then imported that in. I was also having trouble for a long time trying to get the database to be read. I then discovered I needed to use the 'install.packages("readxl")' prompt in order for it to be read.

```{r}
install.packages("readxl")
excel_path <- "/Users/pat/Downloads/DB_excel.xlsx"
cat("Excel", excel_path, "\n")

data <- tryCatch(
  readxl::read_excel(excel_path),
  error = function(e) {
    message("Error reading Excel file: ", e$message)
    NULL
  }
)
if (!is.null(data)) {
  cat("Data successfully read from Excel file.\n")
  print(head(data))
} else {
  cat("Failed to read data from Excel file.\n")
}
```

## Adding in and listing Tables from the Database

```{r}
install.packages("RSQLite")
library(RSQLite)
library(DBI)

db_path <- "/Users/pat/Downloads/DB_excel.xlsx"
conn <- dbConnect(RSQLite::SQLite(), dbname = db_path)

tryCatch({
  projects <- dbGetQuery(conn, 'SELECT * FROM Projects')
  Assets <- dbGetQuery(conn, 'SELECT * FROM Assets')
  Developers <- dbGetQuery(conn, 'SELECT * FROM Developers')
  ProjectDevelopers <- dbGetQuery(conn, 'SELECT * FROM ProjectDevelopers')
  Timelines <- dbGetQuery(conn, 'SELECT * FROM Timelines')
  Customers <- dbGetQuery(conn, 'SELECT * FROM Customers')
  AssetsDevelopers <- dbGetQuery(conn, 'SELECT * FROM AssetsDevelopers')
}, error = function(e) {
  print(paste("Error: ", e$message))
})

```

# Questions

1.  List the total budget allocated for projects in each country, along with the count of projects per country. Display sorted by the total budget in descending order.

    ```{r}

    ```

2.  List the average development time for projects, categorized by the number of assets used.

    ```{r}

    ```

3.  List the top three developers based on the number of successful projects they’ve been involved in. Display the results.

    ```{r}

    ```

## Part A Conclusion 
